---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Lex Drennan"
date: "8/26/2019"
output: 
  html_document: 
    fig_height: 7
    fig_width: 9
    highlight: zenburn
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The database has *3 variables/columns* and *1846 rows*. The variables are *dataset*, *x values* and *y values*. 

### Exercise 2

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Here we see a savage T-Rex, presumably before attempting push ups. 
The relationship between *x* and *y* is r = -0.06447185

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3
Creating a *star* graph...
```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation between *x* and *y* is *r=-0.0629611*. This dataset has slightly more correlation than the dino data set which has an *r=-0.06447185*.

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4
A circle graph....
```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

With a crappy correlation of *r=-0.06834336*.

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

And here are all the datasets within datasaurus_dozen:

```{r}
ggplot(data = datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
```


```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

The most highly correlated data set is *dots r=-0.06034144* followed by *h-lines r=-0.06171484*. 